{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-01-23 documents/background.tex
Dialogue

@@

@@

@@

@@

@@

\footnote{A wave propagating into tissue with $\epsilon=70$ has a refractive index $n=\sqrt{\mu/\epsilon}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$. This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.}

@@

HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
IEEE C95.1-2005 safety standard [n.b. 4.3, Table 9, subsection e. peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis.

@@

@@

Pakhomov \cite{Comparative} expose frog heart cells. No effects on pacemaker at 0.9 kV/m (although the field inside the ).

Note: Not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and not in another.

@@

\subsection{Tsen's femtosecond laser ISRU}

Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. Does not directly act on 
the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.

Unfortunately, these results appear to have failed replication \cite{No2011}. In any case, inactivation requires a very long duration of exposure; unlikely to be of great clinical use.

@@

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.} 
%
, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.

@@

Laser

@@

@@

Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to have a resonance-like peak.

@@

Footnote [At first blush, such an explanation does not seem unreasonable. In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).

@@

In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges from the continuum hypothesis toward zero.]

@@

\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.

>>>>

Note that it is possible that this has already been worked on. The last review was several months ago, and the literature is changing very rapidly.

@@

suggestive, especially because a model organism

An abundance of mechanisms exist to. Irritatingly, such mechanisms have almost universally been ruled out by careful experiment. Many entirely plausible mechanisms exist for which the only valid answer is that they simply do not occur in practice.

@@

formal literature review; In particular no search criteria were defined.

%
\footnote{It may be useful to clarify 'non-thermal'; it caused us some confusion, as the proteins of the virion locally absorb energy and undoubtedly increase in temperature; indeed the same denaturation processes may occur. The key is that, when excited in this manner, the energies in the envelope are poorly modeled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'.} 
%

"Windows" of the same sort have been found, both in thermal and pulsed ultra-high-power UV Prodouz \cite{Use1987a}.

@@

Excellent theoretical arguments against the possibility of non-thermal effects can be found Adair \cite{Vibrational2002}, Adair \cite{Biological2002}, and Foster \cite{Viscous2000} on microtubules.

Adair \cite{Biophysics2000} on Brillouin.

\nameref{sec:viscousdamping}

Data cannot be trusted implicitly. By time-domain spectrometry (a reasonably trustworthy technique), Miura \cite{Microwave1994} find

Owrutsky Vibrational1994

@@

The field strengths are high enough to lead to Townsend breakdowns in air (if the duration is longer than the formative lag). In some sense, we are concerned with field magn

This idea, that resonances, is backed up by measurements by Gabriel; the slowest relaxation time in the microwave regime appear to be in the mammary glands, and. Small resonances will be disguised by the aggregation, however.

Dielectric measurements on different proteins demonstrate that the slowest relaxation

@@

@@

\begin{fquote}[Wait][ \cite{treatyelectromagnetic}]
HFM-189 found no published and replicated adverse health effects or biological mechanisms, beyond
thermal interaction, for pulses shorter than 100 ms which suggested that neither the peak E-field limit in the
IEEE C95.1-2005 safety standard [n.b. chapter 4.3, Table 9, subsection e. peak E field 100 kV/m] nor the proposed limit in the Directive 2004/40/EC [33] (subsequently promulgated as 2013/35/EU [34]) have scientific basis. 
\end{fquote}

@@

\footnote{A wave propagating into tissue with $\epsilon_r=70$ has a refractive index $n=\sqrt{\mu_r/\epsilon_r}$, and is transmitted as $\frac{2 n_1}{n_1 + n_2}$. This is of no concern for waveguide or bolus applicators, since the reflected energy is captured and returned.}

@@

Pakhomov \cite{Comparative} expose frog heart cells, and find no effects on functioning pacemaker cells at 0.9 kV/m (although the field inside the waveguide may be lower).

Note: The author not being biologists or microwave engineers, the trained reader may find that we are too verbose in simple technique and methodology and not detailed in another.

@@

\subsection{Coherent control and laser chemistry}

Man \cite{Picosecond2016b} perform a trustworthy all-atom molecular dynamics simulation of . As with most molecular dynamics simulations, the applied field was enhanced by several orders of magnitude to an unrealistic 2 gigavolts per meter to make the reaction proceed fast enough to be captured without excessive computation time.

\subsection{Picosecond and femtosecond laser studies}

A group of literature exists concerning the excitation of these modes with picosecond or femtosecond lasers. A pulse some 300 fs long and with a carrier of around 600 nm. Impulsive stimulated Raman scattering. We confess to not having studied these mechanisms in great detail. The pulse does not directly act on the vibrational mode; the optimal pulse duration is some small fraction of the period of the mode in question.

M13 is a 880 nm by 6.6 nm rod \cite{M132015}.

Dykeman \cite{Vibrational2009} perform an all-atom molecular dynamics simulation of ISRU of phage M13, albeit without a heat bath to accurately represent damping. An interesting result is that despite the broadband nature of the pulse, \char`~80\% of the pulse energy couples into only 5 modes, starting at approx. 20 GHz. The binding energy is implied to be too high to explain the experimental results.

Zhou \cite{Maximum2010} consider the optimal control theory for this problem.

Unfortunately, the experimental results on M13 appear to have completely failed replication by Wigle \cite{No2011}, and those on lymphocytes do not agree with existing literature by two orders of magnitude \cite{Targeted2002}, observing that over 1 TW of incident power is required to reproduce the effects by .

1 TW / (100 ps / 0.3 ps) = 3 GW

In any case, inactivation through this mechanism appears to require a very long duration of exposure.

@@

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal

, non-chemical technique, harmless for continuous exposure to tissue, which can sterilize air and surfaces alike, including skin, eyes, and within hair; it evolves no ozone, can readily be generated with \$1 USD - scale devices, acts instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}.

@@

@@

\section{Matters to consider in the design of experiments and the evaluation of literature}

@@

Edwards et al in 1984 and 1985 measured the reflection from an open-ended coaxial line dipped in DNA solution and found that DNA appeared to produce a resonance-like peak.

@@

At first blush, such an explanation does not seem unreasonable. In the case of the virus, for instance, the expected amplitude of oscillation for which this mechanism applies is on the order of one water molecule (~0.1 nm).

@@

In the case of a uniform rotating sphere, for instance, the [Einstein - ?] viscous drag force diverges strikingly from the continuum hypothesis toward zero.

@@

\lettrine{U}nfortunately for these hypotheses, Foster 1986, replicating Edwards’ coaxial line method with a more rigorous error analysis on plus an equally rigorous transmission-line absorption, Gabriel, and Bigio in 1993, an ingenious thermo-optical technique, quite definitively demonstrate - to absurd precision -  that the previous results were a characteristic artifact of coaxial-line spectrometry, and that DNA does not have any resonance mode at any microwave frequency.

### 2021-01-23 documents/brillouin_pulse_math.tex
pdftex
Dialogue

\section{The Brillouin precursors}

@@

Such thin

@@

@@

@@

These precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose,

@@

@@

Macke \cite{Simple2012} have come up with a number of other analytic representations for various signals, such as chirped gaussian pulses.

\printendnotes

>>>>

\pagebreak
\section{The Brillouin precursors}

@@

The extremely high losses from such thin coaxial cables should be considered.

@@

Precursors have been used in practice, by Ong \cite{Detection2003} using simple square waves to detect respiration\footnotemark, Ossberger \cite{Noninvasive2004} for the same purpose; and various techniques for breast cancer detection.

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
		\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test1}
	\caption{Second.}
\end{figure}

@@

@@

\paragraph{\textbf{Subharmonics}}\

@@

Macke \cite{Simple2012} have come up with a number of other analytic dispersion representations for various signals, such as chirped gaussian pulses.

%\printendnotes

### 2021-01-23 documents/safety.tex
Stuff and things
Wrote a better abstract
Gelgreen
data
Dialogue

\documentclass[paper.tex]{subfiles}
\begin{document}

@@

@@

@@

\includegraphics[scale=0.5]{cells.png}

@@

There are some 20,000 papers on the topic of RF safety, with solid in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.

>>>>

%!TeX root = safety
\documentclass[paper.tex]{subfiles}
\begin{document}

@@

Manikowska [] "showed a highly significant (P > 0.001)", and "Therefore, under our experimental conditions, effects of heat stress and local heating are unlikely.". Promptly disproved by \cite{Cytogenetic1986}.

@@

We borrow the "teleological why" from \cite{mechanisms1981}.

@@

\begin{figure}[H]
	\includegraphics[scale=0.5]{cells_2x.png}
	\caption{xkcd.com/1217}
\end{figure}

@@

There are some 20,000 papers on the topic of RF safety, with solid mechanistic, in vitro, in vivo and epidemiological evidence of safety in the 2.4 GHz and 5.8 GHz bands.

### 2021-01-23 documents/scan_converter.tex
scan converter, but fucking why
Progress
Dialogue

@@

$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F)/2} $$

@@

>>>>

The very high voltage means that low-sensitivity diagnostics, like lithium niobate optical probes. Not having a suitable optical bench, an electron-beam probe, similar to a streak camera, itself similar in principle to scan-conversion digitizer tubes in Tek SCD and 7912 series transient digitizers.

If a low voltage sensitivity is required, and because modern high-pixel-density CMOS sensors allow the required deflection and the entire structure to be minimized, these are simple to design and inexpensive (much of the complexity being in the slow-wave or travelling-wave structure which is usually required to match the signal velocity to the - slowing down light without affecting its properties or drawing power is an extremely difficult problem) and can offer sample rates in the terasamples/s and analog bandwidths , albeit with low vertical resolution.

original von Ardenne

@@

$$ \frac{\sin(\frac{2\pi F \tau}{2})}{(2\pi F \tau)/2} $$

@@

Image intensifier microchannel plates where angled holes cause secondary electron

### 2021-01-23 documents/viscosity.tex
Progress
Dialogue

@@

However, if we apply the same arguments to microtubules \cite{Viscous2000}, omega_c = 80 GHz, and Q=11.2. The effects of these exposures should have been

>>>>

\section{Viscous damping}
\label{sec:viscousdamping}

@@

However, if we apply the same arguments to microtubules \cite{Viscous2000}, we get $omega_c$ = 80 GHz and Q=11.2. The effects of these exposures should have been noticed in previous studies, so there is probably something gravely wrong with this analysis.

In the steady-state, producing 1 nN from a charge of $10^5$ takes some 60 kV/m.
